---
title: "HW3"
author: "Alice"
date: "2023-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```{r cars}
#HW3

##element1
weight1<-c(104,95,87,77,112)
weight1dou<-as.double(weight1)
typeof(weight1dou)
weight2<-c(96,91,81,75,118)
weight2dou<-as.double(weight2)
typeof(weight2dou)
df<-data.frame(beore_diet=weight1dou,after_diet=weight2dou)
list(df)

##element2
subject<-c("subject_1","subject_2","subject_3","subject_4","subject_5")
rownames(df)<-subject
df
str(subject)
weight_loss<-(weight2-weight1)/weight1*100
str(weight_loss)
table<-data.frame(subject,weight_loss)
list(table)
WEIGHT_LOSS<-list(subject,weight_loss,table)
str(WEIGHT_LOSS)

##element3
message1<-"I was really afraid of coding at first but now I start trying to figure out them step by step."
message2<-"I feel the sense of achievement everytime I finish the assignment :)" 
message<-c(message1,message2) # Amazing, I am glad you can feel that you are progressing. Keep going !

##list
BUBBLE_DIET<-list(df,WEIGHT_LOSS,message)
str(BUBBLE_DIET)
```


